Tidy data structure to support exploration and modeling of temporal data

### 2018-12-03 main.Rmd
added a little bit to index

Time provides a contextual basis for temporal data. A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact data column rather than an attribute, which makes time accessible to users. It is highly advantageous when manipulating time. For example, one could easily extract time components, such as time of day and day of week, from the index to visualize seasonal effects of response variables. One could also join other data sources to the tsibble based on common time indices. The accessibility of tsibble index motivates data analysis towards transparency and human readability. But if the "index" is employed as attributes, analysts would write these simple queries in a programmatic manner, which can be avoidable from an analytic point of view.

@@

Given the nature of temporal ordering, a temporal data set must be sorted by time index as a result. If a key is explicitly declared, the key will be sorted first depending on the ordering of factor levels and the ordering of variables, and followed by arranging time in past-to-future order. The tuberculosis example shows the key is sorted in alphabetic order, followed by ascending years by default, as in Table \@ref(tab:tb-sub). Since time-based operations, for example leading, lagging, or differencing series, require a vector in its time order, the arranged data format assures its validity for these operations without returning unexpected results. There are other possible arrangements in the key, but the baseline is the index (i.e. `year`) ascends within each key element. If any operations on the tidy temporal data results in a deviation from this baseline, it will issue a warning to the users.

It encourage users to look into the data as earlier as possible, assessing the data quality issues.

>>>>

Time provides a contextual basis for temporal data. A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact data column rather than a masked attribute, which makes time visible and accessible to users. It is highly advantageous when manipulating time. For example, one could easily extract time components, such as time of day and day of week, from the index to visualize seasonal effects of response variables. One could also join other data sources to the tsibble based on common time indices. The accessibility of tsibble index motivates data analysis towards transparency and human readability. When the "index" used to be employed as meta information, it created an obstacle for analysts to write these simple queries in a programmatic manner, which should be discouraged from an analytic point of view.

A variable number of time representation is spotted in the wild. Date-time, universally accepted across systems, is the most commonly used type for representing time. Date-time also typically associates with a time zone with adjustments like summer time. This diversity and time zone is respected and taken into consideration for the *tsibble*'s index.

@@
